---
title: "Sri Lanka's Research Impact: A Visual Exploration of Citation Indicators"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    storyboard: true
---

<!-- Google tag (gtag.js) -->
<script async src="https://www.googletagmanager.com/gtag/js?id=G-3LKGJ7KPKZ"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());

  gtag('config', 'G-3LKGJ7KPKZ');
</script>

```{r setup, include=FALSE}
#statistics.mart.tst
library(flexdashboard)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(here)
library(plotly)
library(patchwork)
library(janitor) # remove white space in columns
```

```{r}
# colours
color_ins <- c("University of Sri Jayewardenepura"="red",                     "International Water Management Institute (IWMI)" = "#1f78b4",             "University of Peradeniya" = "#a6cee3",       "Wayamba University of Sri Lanka"  = "#b2df8a",
"National Institute of Fundamental Studies, Sri Lanka" = "#33a02c","Rajarata University of Sri Lanka" = "#fb9a99",  "University of Jaffna"   = "#fdbf6f",                             "Munasinghe Institute for Development (MIND)" = "#ff7f00",          "University of Kelaniya"  = "#cab2d6",                               "University of Colombo" = "#6a3d9a")
```

```{r}
# data
career <- read_excel(here("data", "Table_1_Authors_career_2022_pubs_since_1788_wopp_extracted_202310.xlsx"), sheet=2)
career$inst_name <- recode_factor(career$inst_name,"International Water Management Institute" = "International Water Management Institute (IWMI)"  , 
                               "Faculty of Medicine, University of Peradeniya"= "University of Peradeniya", "University of Colombo Faculty of Medicine"=   "University of Colombo" ,"International Water Management Institute (IWMI) Colombo" = 
"International Water Management Institute (IWMI)") 
career_lka <- career |> filter(cntry=="lka")
singleyr <- read_excel(here("data", "Table_1_Authors_singleyr_2022_pubs_since_1788_wopp_extracted_202310.xlsx"), sheet=2)
singleyr$inst_name <- recode_factor(singleyr$inst_name, "International Water Management Institute" = "International Water Management Institute (IWMI)"  , 
                               "Faculty of Medicine, University of Peradeniya"= "University of Peradeniya", "University of Colombo Faculty of Medicine"=   "University of Colombo" ,"International Water Management Institute (IWMI) Colombo" = 
"International Water Management Institute (IWMI)")
singleyr_lka <- singleyr |> filter(cntry=="lka")
```

# USJ Highlights

Column {data-width=400}
-----------------------------------------------

### Figure 1: Single recent year data pertain to citations received during calendar year 2022

```{r, fig.height=5}
singleyr_lka  |>
	group_by(inst_name) |>
	summarise(count = n()) |> 
	ggplot(aes(x = reorder(inst_name,(-count)), y = count, fill=I(ifelse(inst_name=="University of Sri Jayewardenepura", "red", "black")))) + 
		geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + xlab("")+xlab("Institution name") + ylab("Number of authors")
```


### Figure 2: Career-long data are updated to end-of-2022

```{r, fig.height=5}
career_lka |>
	group_by(inst_name) |>
	summarise(count = n()) |> 
	ggplot(aes(x = reorder(inst_name,(-count)), y = count, fill=I(ifelse(inst_name=="University of Sri Jayewardenepura", "red", "black")))) + 
		geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + xlab("Institution name") + ylab("Number of authors")
```





Column {data-width=300}
-----------------------------------------------------------------------

### Figure 3: Rank based on composite score with data from calendar year 2022 (self-citation excluded)

```{r, fig.height=12}
singleyr_lka_filter <- singleyr_lka |>
  select(c("authfull", "inst_name", "rank"))
career_lka_filter <- career_lka |>
  select(c("authfull", "inst_name", "rank"))
p1 <- ggplot(data=singleyr_lka_filter,
       aes(y=reorder(authfull,(-rank)), x = rank, colour=I(ifelse(inst_name=="University of Sri Jayewardenepura", "red", "black")))) + geom_point() + geom_segment(aes(yend = reorder(authfull,(-rank))), xend = 0, colour = "grey50") + ylab("Author name") + xlab("Rank") + scale_x_continuous(labels = scales::comma_format()) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
p1.2 <- plotly::ggplotly(p1, tooltip = c("rank")) |> style(showlegend = FALSE)

p1.2



```

Column {data-width=300}
-----------------------------------------------------------------------

### Figure 4: Rank based on composite score with data from career-long data (self-citation excluded)

```{r, fig.height=12}
p2 <- ggplot(data=career_lka_filter,
       aes(y=reorder(authfull,(-rank)), x = rank, col=I(ifelse(inst_name=="University of Sri Jayewardenepura", "red", "black")))) + geom_point() +   geom_segment(aes(yend = reorder(authfull,(-rank))), xend = 0, colour = "grey50") +
  ylab("Author name") + xlab("Rank")  + scale_x_continuous(labels = scales::comma_format()) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
#p3 <- ggplot(career_lka_filter, aes(y=reorder(authfull,(-rank)), x = "1", fill = inst_name)) +
#  geom_tile() + theme(legend.position ="none",axis.text.y=element_blank(), 
#      axis.ticks.y=element_blank()) +ylab("")
p4 <- ggplotly(p2, tooltip = c("rank"))
p4 |> style(showlegend = FALSE)
```



# Authors by institution: calendar year 2022 data

Column {data-width=300}
-----------------------------------------------------------------------

### Figure 5: Rank based on composite score: 2022 calender year data (self-citation excluded)

```{r, fig.height=12}
a1 <- ggplot(data=singleyr_lka_filter,
       aes(y=reorder(authfull,(-rank)), x = rank, col=inst_name)) + geom_point() +   geom_segment(aes(yend = reorder(authfull,(-rank)), col = inst_name), xend = 0 ) +
  ylab("Author name") + xlab("Rank")  + scale_x_continuous(labels = scales::comma_format(), breaks=seq(10000, 550000, 20000)) +
  scale_color_manual(values = color_ins) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

a2 <- ggplotly(a1, tooltip = c("rank", "inst_name"))
a2 |> style(showlegend = TRUE)
```



# Authors by institution: Career-long data

Column {data-width=300}
-----------------------------------------------------------------------

### Figure 6: Rank based on composite score: career-long data (self-citation excluded)

```{r, fig.height=12}

b1 <- ggplot(data=career_lka_filter,
       aes(y=reorder(authfull,(-rank)), x = rank, col=inst_name)) + geom_point() +   geom_segment(aes(yend = reorder(authfull,(-rank)),col = inst_name), xend = 0) +
  ylab("Author name") + xlab("Rank")  + scale_x_continuous(labels = scales::comma_format(), breaks=seq(65000, 440000, 10000)) + scale_color_manual(values = color_ins) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 

b2 <- ggplotly(b1, tooltip = c("rank", "inst_name"))
b2 |> style(showlegend = TRUE)
```


# Author profiles: with data from calendar year 2022 data

Column {data-width=300}
-----------------------------------------------------------------------

```{r, fig.height=8}
singleyr_lka2 <- singleyr_lka
singleyr_lka2 <- clean_names(singleyr_lka2)
s1 <- ggplot(data=singleyr_lka2,
       aes(y=reorder(authfull,(nc2222_ns)), x = nc2222_ns, col=inst_name)) + geom_point()   + xlab("Total cites in 2022") + scale_color_manual(values = color_ins) + theme(legend.position="none", axis.text.y = element_text(size = 6)) + ylab("")

s2 <- ggplot(data=singleyr_lka2,
       aes(y=reorder(authfull,(h22_ns)), x = h22_ns, col=inst_name)) + geom_point() +    xlab("h-index as of end 2022") + scale_color_manual(values = color_ins) + theme(legend.position="none", axis.text.y = element_text(size = 6)) + ylab("")

```

### Figure 7: Total cites in 2022 (self-citations excluded)

```{r, fig.height=8}
ggplotly(s1, tooltip = c("inst_name","nc2222_ns"))
```

### Figure 10: hm-index as of end 2022 (self-citations excluded)

```{r, fig.height=8}
s4 <- ggplot(data=singleyr_lka2,
       aes(y=reorder(authfull,(hm22_ns)), x = hm22_ns, col=inst_name)) + geom_point() +    xlab("hm-index as of end 2022") + scale_color_manual(values = color_ins) + theme(legend.position="none", axis.text.y = element_text(size = 6)) + ylab("")
ggplotly(s4, tooltip = c("inst_name","hm22_ns"))
```

Column {data-width=300}
-----------------------------------------------------------------------

### Figure 8: h-index as of end 2022 (self-citations excluded)

```{r, fig.height=8}
ggplotly(s2, tooltip = c("inst_name","h22_ns"))
```


### Figure 11: Number of single authored papers

```{r,fig.height=8}
s5 <- ggplot(data=singleyr_lka2,
       aes(y=reorder(authfull,(nps_ns)), x = nps_ns, col=inst_name)) + geom_point() +    xlab("Number of single authored papers") + scale_color_manual(values = color_ins) + theme(legend.position="none", axis.text.y = element_text(size = 6)) + ylab("")
ggplotly(s5, tooltip = c("inst_name","nps_ns"))
```

Column {data-width=300}
-----------------------------------------------------------------------

### Figure 9: Composite score (self-citations excluded)

```{r, fig.height=8}
s3 <- ggplot(data=singleyr_lka2,
       aes(y=reorder(authfull,(c_ns)), x = c_ns, col=inst_name)) + geom_point() +    xlab("Composite score") + scale_color_manual(values = color_ins)+theme(legend.position="none", axis.text.y = element_text(size = 6)) + ylab("")
ggplotly(s3, tooltip = c("inst_name","c_ns"))
```

### Figure 12: Total cites to single authored papers (self-citations excluded)

```{r, fig.height=8}
s6 <- ggplot(data=singleyr_lka2,
       aes(y=reorder(authfull,(ncs_ns)), x = ncs_ns, col=inst_name)) + geom_point() +    xlab("Total cites to single authored papers") + scale_color_manual(values = color_ins) + theme(legend.position="none", axis.text.y = element_text(size = 6)) + ylab("")
ggplotly(s6, tooltip = c("inst_name","ncs_ns"))
```

# Author profiles: career-long data

Column {data-width=300}
-----------------------------------------------------------------------

```{r, fig.height=8}
career_lka2 <- clean_names(career_lka)
c1 <- ggplot(data=career_lka2,
       aes(y=reorder(authfull,(nc9622_ns)), x = nc9622_ns, col=inst_name)) + geom_point()   + xlab("Total cites 1996-2022") + scale_color_manual(values = color_ins) + theme(legend.position="none") + ylab("")

c2 <- ggplot(data=career_lka2,
       aes(y=reorder(authfull,(h22_ns)), x = h22_ns, col=inst_name)) + geom_point() +    xlab("h-index as of end 2022") + scale_color_manual(values = color_ins) + theme(legend.position="none") + ylab("")

```

### Figure 13: Total cites 1996-2022 (self-citations excluded)

```{r, fig.height=8}
ggplotly(c1, tooltip=c("inst_name","nc9622_ns"))
```

### Figure 16: hm-index as of end 2022 (self-citations excluded)

```{r, fig.height=8}
c4 <- ggplot(data=career_lka2,
       aes(y=reorder(authfull,(hm22_ns)), x = hm22_ns, col=inst_name)) + geom_point() +    xlab("hm-index as of end 2022") + scale_color_manual(values = color_ins) + theme(legend.position="none") + ylab("")
ggplotly(c4, tooltip = c("inst_name","hm22_ns"))
```

Column {data-width=300}
-----------------------------------------------------------------------

### Figure 14: h-index as of end 2022 (self-citations excluded)

```{r, fig.height=8}
ggplotly(c2, tooltip = c("inst_name","h22_ns"))
```


### Figure 17: Number of single authored papers

```{r,fig.height=8}
c5 <- ggplot(data=career_lka2,
       aes(y=reorder(authfull,(nps_ns)), x = nps_ns, col=inst_name)) + geom_point() +    xlab("Number of single authored papers") + scale_color_manual(values = color_ins) + theme(legend.position="none") + ylab("")
ggplotly(c5, tooltip = c("inst_name","nps_ns"))
```

Column {data-width=300}
-----------------------------------------------------------------------

### Figure 15: Composite score (self-citations excluded)

```{r, fig.height=8}
c3 <- ggplot(data=career_lka2,
       aes(y=reorder(authfull,(c_ns)), x = c_ns, col=inst_name)) + geom_point() +    xlab("Composite score") + scale_color_manual(values = color_ins)+theme(legend.position="none") + ylab("")
ggplotly(c3, tooltip = c("inst_name","c_ns"))
```

### Figure 18: Total cites to single authored papers (self-citations excluded)

```{r, fig.height=8}
c6 <- ggplot(data=career_lka2,
       aes(y=reorder(authfull,(ncs_ns)), x = ncs_ns, col=inst_name)) + geom_point() +    xlab("Total cites to single authored papers") + scale_color_manual(values = color_ins) + theme(legend.position="none") + ylab("")
ggplotly(c6, tooltip = c("inst_name","ncs_ns"))
```

# Author field


### Top ranked higher-level Science-Metrix category (field) for author: based on calendar year 2022 data

```{r,fig.width=20}
singleyr_lka2  |>
	group_by(sm_field, inst_name) |>
	summarise(count = n()) |> 
	ggplot(aes(x = reorder(sm_field,(-count)), y = count, fill=sm_field)) + 
		geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position="bottom") + xlab("Field") + ylab("Number of authors") + facet_wrap(vars(inst_name), ncol=10,scale="free_x", labeller = label_wrap_gen(multi_line = TRUE)) + scale_fill_brewer(palette = "Paired") + labs(fill = "Top ranked higher-level Science-Metrix category (field) for author")
```


### Author name vs Author field 

```{r, fig.width=20, fig.height=5}
singleyr_lka2  |> 
  group_by(sm_field, authfull) |>
	summarise(count = n()) |>
  ggplot(aes(x = authfull, y = sm_field, fill = count)) +
  geom_raster(color = "white") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "none") + xlab("")+ylab("")+ coord_fixed(ratio = 0.8)
```

# About

**References**

Ioannidis, John P.A. (2023), October 2023 data-update for "Updated science-wide author databases of standardized citation indicators", Elsevier Data Repository, V6, doi: 10.17632/btchxktzyw.6

**Prepared by:** [Dr Thiyanga S. Talagala](https://thiyanga.netlify.app/)

**email:** ttalagala@sjp.ac.lk

**Last updated: ** 12 October 2023